\documentclass[11pt,a4paper]{article}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=2.5cm}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\bstar}{\beta^*}
\newcommand{\dpair}{\delta_{\mathrm{pair}}}
\newcommand{\Ntrl}{\mathcal{N}_{\mathrm{trl}}}
\newcommand{\Aadm}{\mathcal{A}}
\newcommand{\Obs}{\mathcal{O}}
\newcommand{\GBI}{G_{\mathrm{BI}}}
\newcommand{\SBI}{S_{\mathrm{BI}}}
\newcommand{\ImH}{\operatorname{Im}\mathbb{H}}
\newcommand{\cchi}{c_\chi}

\begin{document}

  \title{Vertical Non-Injectivity and the Stability of the Observable Rank:\\
  Closing the Unconditional Transfer
    $c_\chi \to \delta_{\mathrm{pair}} \to \beta^*$\\[6pt]
    {\large O24 --- Spectral Admissibility Sub-programme}}

  \author{J\'er\^ome Beau\\
  \small Independent Researcher\\
  \small \href{mailto:jerome.beau@cosmochrony.org}{jerome.beau@cosmochrony.org}}

  \date{2026}

  \maketitle

  \begin{abstract}
    O18~\cite{Beau2026a22} established the minimal fibre condition: Born--Infeld parity is the
    only global symmetry of $\SBI[\chi]$, ensuring that each fibre of the non-injective projection
    $\Pi$ is exactly $\{\chi, -\chi\}$.
    O22~\cite{Beau2026a26} proved the shell-alignment conjecture of O21~\cite{Beau2026a25},
    and O23~\cite{Beau2026a27} derived the threshold condition $\Sigma_c(n_3) = 3$ from the
    quaternionic maximality of the admissible neutral traceless sector.
    Together, these results show that the integer~$3$ in $\Sigma_c(n_3) = 3$ is a property of
    $\operatorname{Im}\Pi \cap \Ntrl$, not of the cardinality of the fibres.
    The condition of O18 is therefore stronger than necessary: the programme requires only that
    any symmetry of $\SBI$ acts \emph{vertically} with respect to $\Pi$, i.e.\ does not enlarge
    the real rank of the admissible neutral traceless sector.
    The present paper proves this \emph{verticality condition} directly from Born--Infeld
    admissibility and the quaternionic maximality established in~O23, without requiring a
    classification of $\mathcal{C}_{\mathrm{eff}}$.
    As a corollary, the transfer chain
    \[
      \cchi \;\longrightarrow\; \dpair \;\longrightarrow\;
      \bstar = \frac{1}{\dpair + \tfrac{1}{2}} \approx 0.126
    \]
    is established unconditionally with respect to the fibre structure of~$\Pi$.
    Non-injectivity may increase microscopic multiplicity, but cannot enlarge the admissible
    observable structure.
  \end{abstract}

  \medskip
  \noindent\textbf{Keywords.}
  Cosmochrony; spectral admissibility; non-injective projection; verticality condition;
  observable rank stability; quaternionic maximality; Born--Infeld constraint;
  fibre structure; cascade exponent~$\bstar$

  \clearpage
  \tableofcontents

  \clearpage
  \section{Position of the Problem after O22--O23}
    \label{sec:position}

    \subsection{What O18 required and why it was sufficient but not necessary}
      \label{sec:o18}

      O18~\cite{Beau2026a22} derived the minimal fibre structure of the non-injective projection
      $\Pi$ from the parity of the Born--Infeld action $\SBI[\chi]$.
      Its central result (Theorem~3.3 of O18) states that the fibre of $\Pi$ above any
      observable $o \in \Obs$ contains at least the orbit $\{\chi, -\chi\}$, and that this orbit
      is the \emph{minimal} fibre under the assumption that Born--Infeld parity is the only global
      effective symmetry of $\SBI$.
      Remark~2.6 of O18 acknowledged explicitly that in an enriched framework admitting additional
      symmetries, the fibre could be larger.

      The condition ``parity is the only symmetry'' was introduced to guarantee minimality of the
      fibre.
      It was sufficient for the programme at the time: a minimal fibre $\{\chi, -\chi\}$ ensures
      that the non-injectivity of $\Pi$ does not create additional observable directions beyond those
      already present.
      However, it is stronger than necessary.
      The programme does not require small fibres; it requires that additional fibre structure, if
      present, be \emph{invisible at the level of admissible observables}.

    \subsection{The key distinction: fibre cardinality versus observable rank}
      \label{sec:distinction}

      The results of O22 and O23 clarify the precise invariant that controls the chain
      $\cchi \to \dpair \to \bstar$.
      O23~\cite{Beau2026a27} identifies this invariant as
      \[
        \dim_{\mathbb{R}}\bigl(\operatorname{Im}\Pi \cap \Ntrl\bigr) = 3,
      \]
      where $\Ntrl$ denotes the admissible neutral traceless sector.
      This is a property of the \emph{image} of $\Pi$, not of its fibres.
      The integer~$3$ is the real dimension of the imaginary quaternionic subspace $\ImH$,
      identified in O23 as the unique maximal admissible associative non-commutative structure
      compatible with Born--Infeld parity.

      Two configurations that lie in the same fibre of $\Pi$ are, by definition, mapped to the same
      observable.
      Whether the fibre contains two elements or a continuum, the image of $\Pi$ --- and hence the
      admissible observable structure --- is unchanged.
      The cardinality of the fibres and the rank of the image are therefore independent quantities,
      and it is the rank that governs the mechanism.

    \subsection{The two levels of $\Pi$: kernel and image}
      \label{sec:twolevels}

      The projection $\Pi$ admits a natural decomposition into two structurally distinct levels.

      The \emph{kernel level} $\ker\Pi$ encodes the microscopic multiplicity: the set of substrate
      configurations $\chi$ that are indistinguishable at the level of admissible observables.
      A larger kernel means more microscopic configurations projecting to the same effective state.
      This does not generate new observable directions; it generates projection residuals, i.e.\
      substrate degrees of freedom that are compressed by $\Pi$ and manifest as fluctuations in
      the effective description.

      The \emph{image level} $\operatorname{Im}\Pi$ encodes the effective observable structure: the
      set of states that are distinguishable by at least one admissible observable.
      Its intersection with $\Ntrl$ has real rank~$3$ by O23, and this rank is what enters the
      threshold condition $\Sigma_c(n_3) = 3$ and, downstream, the transfer
      $\dpair \to \bstar \approx 0.126$.

      The key structural principle is:
      \begin{quote}
        \emph{Fluctuations and observables coexist in the same effective space.
        More residuals do not add new directions to that space; they increase the amplitude of
        projection noise within the directions already present.}
      \end{quote}

    \subsection{Scope of O24}
      \label{sec:scope}

      The present paper proves the \emph{verticality condition}: every symmetry of $\SBI$
      compatible with admissibility acts vertically with respect to $\Pi$, in the sense that it
      does not increase the real rank of $\operatorname{Im}\Pi \cap \Ntrl$.
      The proof uses the quaternionic maximality established in O23 as its central ingredient and
      does not require a global classification of $\mathcal{C}_{\mathrm{eff}}$.

      The paper does not address the remaining open task of the programme: the extended numerical
      campaign at large primes $q \in \{101, 151, 211\}$ across multiple conjugate pairs, required
      to confirm the shell-alignment prediction and reduce the residual distance
      $\mathrm{dist}(n_3^{\mathrm{obs}}, \mathbb{Z}) \approx 0.20$ observed at $q = 61$.

  \section{The Observable Rank as the Invariant of the Chain}
    \label{sec:rank}

    \subsection{Recapitulation: maximality from O23}
      \label{sec:o23recap}

      We recall the central result of O23~\cite{Beau2026a27}.

      \begin{theorem}[O23 Theorem~3.2, Three stable directions from quaternionic maximality]
        \label{thm:o23}
        Let $\Pi\colon \chi \to \Obs$ be a non-injective projection compatible with the
        Born--Infeld constraint, admitting a Weil realisation on $\mathrm{Heis}_3(\mathbb{Z}/q\mathbb{Z})$.
        The admissible neutral traceless sector is identified with $\ImH$.
        The real rank of $\operatorname{Im}\Pi \cap \Ntrl$ is exactly~$3$.
        Moreover, this rank is \emph{maximal}: $\ImH$ is the unique maximal admissible associative
        non-commutative structure compatible with Born--Infeld parity, and no admissible realisation
        of the neutral sector can have real rank greater than~$3$.
        Consequently, $\Sigma_c(n_3) = 3$.
      \end{theorem}

      The maximality statement is essential.
      O23 does not merely establish the \emph{existence} of a quaternionic structure of rank~$3$; it
      establishes that no admissible structure compatible with Born--Infeld parity can have a
      higher rank.
      This maximality is what makes the verticality argument of Section~\ref{sec:verticality}
      non-circular.

    \subsection{Independence of the observable rank from the fibre structure}
      \label{sec:independence}

      The following lemma makes the rank--kernel decoupling explicit.

      \begin{lemma}[Rank--kernel decoupling]
        \label{lem:decoupling}
        The real rank of $\operatorname{Im}\Pi \cap \Ntrl$ is independent of the cardinality of
        $\ker\Pi$.
      \end{lemma}

      \begin{proof}
        The rank is a property of the image of $\Pi$ as a linear map; it is determined by the dimension
        of the span of $\Pi(\Aadm)$ within $\Ntrl$.
        Enlarging $\ker\Pi$ --- i.e.\ increasing the number of substrate configurations that project to
        the same observable --- leaves the image $\Pi(\Aadm)$ and its intersection with $\Ntrl$
        unchanged.
        The rank therefore depends only on the structure of $\operatorname{Im}\Pi$, not on the
        structure of $\ker\Pi$.
      \end{proof}

      \begin{remark}
        Lemma~\ref{lem:decoupling} is linear-algebraic and holds independently of any assumption on
        the symmetry group $\GBI$.
        It records the conceptual separation between the two levels of $\Pi$ identified in
        Section~\ref{sec:twolevels}: kernel structure governs microscopic multiplicity and
        fluctuation amplitude; image structure governs the observable mechanism.
      \end{remark}

    \subsection{Residuals and fluctuations as kernel-level phenomena}
      \label{sec:residuals}

      When the fibre of $\Pi$ above an observable $o$ contains more than the minimal orbit
      $\{\chi, -\chi\}$, the additional configurations constitute substrate degrees of freedom that
      are invisible to admissible observables.
      These degrees of freedom are not lost; they appear as projection residuals in the effective
      description.

      Formally, let $F_o = \Pi^{-1}(o)$ be the fibre above $o$.
      The projection decomposes as
      \[
        \chi = \chi_{\parallel} + \chi_{\perp},
      \]
      where $\chi_{\parallel}$ is the component of $\chi$ in the directions visible to $\Pi$
      (i.e.\ transverse to $\ker\Pi$) and $\chi_{\perp} \in \ker\Pi$ is the residual.
      The observable $o = \Pi(\chi)$ depends only on $\chi_{\parallel}$.
      A larger fibre means a larger space of possible $\chi_{\perp}$ values; it does not modify
      the effective dynamics of $\chi_{\parallel}$.

      In particular, the cascade exponent $\dpair$, the saturation rank $n_3$, and the transfer
      $\dpair \to \bstar$ all operate at the level of $\chi_{\parallel}$ --- the observable sector.
      Projection residuals $\chi_{\perp}$ appear as fluctuations around the effective dynamics but
      do not alter the mechanism.
      Fluctuations and observables coexist in the same effective space; additional residuals
      increase the noise amplitude within that space --- its statistical occupation measure ---
      not its dimensionality.
      This is consistent with the identification in O14~\cite{Beau2026a18} Section~6.4 of the
      residual correction $\epsilon(q)$ as the observable imprint of projection residuals, controlled
      by the phase variance $\mathrm{Var}(\theta)(q)$: more residuals shift the statistical weight
      within the observable space, leaving its rank unchanged.

  \section{The Verticality Lemma}
    \label{sec:verticality}

    \subsection{Setup and statement}
      \label{sec:setup}

      Let $\GBI$ denote the group of symmetries of $\SBI[\chi]$ compatible with Born--Infeld
      admissibility.
      A symmetry $g \in \GBI$ is said to be \emph{admissible} if $g(\Aadm) \subset \Aadm$, i.e.\
      it maps the admissible sector to itself.
      All elements of $\GBI$ are admissible by definition; the property is stated explicitly here
      because it is the key hypothesis used in the proof of Lemma~\ref{lem:verticality}.
      A symmetry $g \in \GBI$ is said to act \emph{vertically} with respect to $\Pi$ if it maps
      each fibre $\Pi^{-1}(o)$ to itself, i.e.\ $\Pi(g\chi) = \Pi(\chi)$ for all $\chi \in \Aadm$.
      A symmetry acts \emph{transversally} if there exists $\chi \in \Aadm$ such that
      $\Pi(g\chi) \neq \Pi(\chi)$, and moreover
      $\Pi(g\chi) \notin \mathrm{span}\bigl(\Pi(\Aadm)\bigr)$.

      A transversal symmetry therefore generates a new linearly independent direction in
      $\operatorname{Im}\Pi \cap \Ntrl$: it strictly increases the real rank of
      $\operatorname{Im}\Pi \cap \Ntrl$.

      \begin{lemma}[Verticality of admissible symmetries]
        \label{lem:verticality}
        Let $g \in \GBI$ be a symmetry of $\SBI[\chi]$ compatible with Born--Infeld admissibility.
        Then $g$ acts vertically with respect to $\Pi$: it does not increase the real rank of
        $\operatorname{Im}\Pi \cap \Ntrl$.
      \end{lemma}

      \begin{proof}
        Suppose for contradiction that $g$ acts transversally.
        Then $g$ generates a new linearly independent direction in
        $\operatorname{Im}\Pi \cap \Ntrl$.

        Since $g \in \GBI$ is admissible, $g(\Aadm) = \Aadm$: any vector generated by the action
        of $g$ on $\Aadm$ remains in $\Aadm$, and in particular satisfies the Born--Infeld
        admissibility constraint.
        Such a direction therefore belongs to the admissible neutral traceless sector characterised
        in Theorem~\ref{thm:o23}.

        But Theorem~\ref{thm:o23} (O23) establishes that the admissible neutral traceless sector has
        \emph{maximal} real rank~$3$: $\ImH$ is the unique maximal admissible associative
        non-commutative structure compatible with Born--Infeld parity.
        A transversal symmetry generating a 4th independent admissible direction would contradict
        this maximality.
        The contradiction shows that $g$ cannot act transversally.
        Therefore $g$ acts vertically.
        Thus, no admissible symmetry can increase the dimension of $\operatorname{Im}\Pi \cap \Ntrl$.
      \end{proof}

    \subsection{Case analysis}
      \label{sec:cases}

      The proof of Lemma~\ref{lem:verticality} proceeds by contradiction and applies uniformly to
      all $g \in \GBI$.
      For clarity, we spell out how the argument applies to the three natural candidate classes of
      additional symmetries identified in O18 Remark~2.6 and O23 Section~5.2.

      \paragraph{Case 1: Parity $\chi \mapsto -\chi$.}
        This is the symmetry established in O18~\cite{Beau2026a22}.
        It maps the fibre $\{\chi, -\chi\}$ to itself and is therefore vertical by definition.
        It does not generate any new direction in $\operatorname{Im}\Pi$.

      \paragraph{Case 2: Phase rotation $\chi \mapsto e^{i\theta}\chi$.}
        The substrate field $\chi$ is real by construction in the Cosmochrony
        framework~\cite{Cosmochrony}.
        A U(1) phase rotation is therefore not a symmetry of $\SBI[\chi]$ for $\theta \notin \pi\mathbb{Z}$,
        and reduces to parity for $\theta = \pi$.
        This class of symmetries does not arise.
        Even if the field were complexified, such a symmetry would act within fibres unless it generated
        new independent admissible neutral traceless directions; but any such directions would be
        excluded by Lemma~\ref{lem:verticality} via the maximality of O23.

      \paragraph{Case 3: Topological symmetries.}
        The Topological Invariants paper~\cite{Beau2026k} establishes that admissible configurations
        are classified by discrete topological invariants (winding number, spin structure) that
        distinguish configurations with distinct invariant values.
        Configurations with different topological invariants are therefore distinguishable by $\Pi$;
        they do not lie in the same fibre and cannot be related by a fibre-preserving symmetry.
        Any topological symmetry that would identify configurations of different winding number would
        contradict the discrete classification of~\cite{Beau2026k}.
        Such symmetries are therefore absent from $\GBI$.

        In each case, the conclusion is consistent with Lemma~\ref{lem:verticality}: no element of
        $\GBI$ acts transversally.

  \subsection{Remark on the non-classificatory character of the argument}
    \label{sec:nonclassif}

    The proof of Lemma~\ref{lem:verticality} does not enumerate all possible symmetries of
    $\SBI$.
    It instead uses the maximality of O23 as a structural obstruction: any transversal symmetry
    would produce an admissible direction of rank greater than~$3$, which is impossible.
    This argument is therefore independent of a global classification of $\mathcal{C}_{\mathrm{eff}}$
    and avoids the topological difficulty identified in Remark~4.2 of~\cite{Beau2026k}.

  \section{Main Results}
  \label{sec:main}

  \subsection{Observable rank stability}
    \label{sec:rankstability}

    \begin{theorem}[Observable rank stability]
      \label{thm:rankstability}
      Under the Born--Infeld constraint and the Weil realisation on
      $\mathrm{Heis}_3(\mathbb{Z}/q\mathbb{Z})$, the real rank of the admissible neutral traceless
      observable sector $\operatorname{Im}\Pi \cap \Ntrl$ is fixed to~$3$ as a structural invariant of
      the admissible sector, independently of the cardinality of the fibres of~$\Pi$.
      Consequently, $\Sigma_c(n_3) = 3$ holds unconditionally with respect to the fibre
      structure of~$\Pi$.
      In particular, no admissible enlargement of $\ker\Pi$ can induce any increase in the
      observable rank.
    \end{theorem}

    \begin{proof}
      By Lemma~\ref{lem:decoupling}, the rank of $\operatorname{Im}\Pi \cap \Ntrl$ is independent of
      $|\ker\Pi|$.
      By Lemma~\ref{lem:verticality}, every $g \in \GBI$ acts vertically and therefore does not
      increase this rank.
      By Theorem~\ref{thm:o23} (O23), the rank is rigidly fixed to~$3$.
      The combination of these three results gives the claim.
      The threshold condition $\Sigma_c(n_3) = 3$ is the observable signature of this rank, as
      established in O23~\cite{Beau2026a27} Section~4.3.
    \end{proof}

  \subsection{Unconditional transfer}
    \label{sec:transfer}

    \begin{corollary}[Unconditional transfer $\cchi \to \dpair \to \bstar$]
      \label{cor:transfer}
      The chain
      \[
        \cchi \;\longrightarrow\; \dpair \;\longrightarrow\;
        \bstar = \frac{1}{\dpair + \tfrac{1}{2}} \approx 0.126
      \]
      is independent of the cardinality of the fibres of $\Pi$.
      The conditionality of O18 Theorem~3.3 --- which required parity to be the only symmetry
      of $\SBI$ --- is resolved: the result holds for any $\GBI$-symmetric non-injective projection,
      provided the verticality condition of Lemma~\ref{lem:verticality} is satisfied.
      The verticality condition is itself a consequence of the Born--Infeld admissibility constraint
      and the quaternionic maximality of O23; it requires no additional hypothesis.
    \end{corollary}

    \begin{proof}
      The chain $\cchi \to \dpair \to \bstar$ was established conditionally in
      O21~\cite{Beau2026a25} Theorem~5.1, under the shell-alignment conjecture and the condition
      that $\Sigma_c(n_3) = 3$.
      O22~\cite{Beau2026a26} proved the shell-alignment conjecture (projection locking forces
      saturation onto a BFS shell).
      Theorem~\ref{thm:rankstability} establishes $\Sigma_c(n_3) = 3$ unconditionally with respect
      to the fibre structure.
      The two conditions of O21 Theorem~5.1 are therefore both satisfied unconditionally, and the
      transfer follows.
    \end{proof}

    \begin{remark}
      Corollary~\ref{cor:transfer} does not remove the numerical open direction.
      The value $\dpair \approx 7.44$ and the shell distance $\mathrm{dist}(n_3^{\mathrm{obs}},
      \mathbb{Z}) \approx 0.20$ at $q = 61$ are numerical results requiring confirmation at larger
      primes $q \in \{101, 151, 211\}$ across multiple conjugate pairs.
      The present result establishes the structural integrity of the chain, not its quantitative
      precision.
    \end{remark}

  \section{Discussion}
  \label{sec:discussion}

  \subsection{What O24 closes and what it does not}
    \label{sec:closes}

    The present paper closes the last structural conditionality in the chain
    $\cchi \to \dpair \to \bstar$.
    The three open problems identified across O21--O23 are now resolved at the structural level:

    \begin{center}
      \begin{tabular}{lll}
        \hline
        Condition & Origin & Status after O24 \\
        \hline
        Shell-alignment conjecture & O21 Conj.~4.1 & Resolved by O22 \\
        $\Sigma_c(n_3) = 3$ & O21 open problem~2 & Resolved by O23 \\
        Parity = only symmetry of $\SBI$ & O18 Rem.~2.6 & Replaced by verticality, \\
        & & proved in O24 \\
        \hline
      \end{tabular}
    \end{center}

    What remains open is the extended numerical programme: computing $n_3^{\mathrm{obs}}$ for all
    conjugate pairs with $\dpair \in [7.4, 10.6]$ across $q \in \{101, 151, 211\}$ using the
    canonical pair observable of O19~\cite{Beau2026a23}, as described in O22~\cite{Beau2026a26}
    Section~6.2.

  \subsection{Relation to O18: necessary versus sufficient}
    \label{sec:o18relation}

    The condition of O18 --- parity is the only global symmetry of $\SBI$ --- was a sufficient
    condition for the programme at the time it was formulated.
    It guaranteed that fibres are minimal, which implies in particular that no additional
    observable directions are created.

    The present paper identifies the \emph{necessary} condition: verticality of all admissible
    symmetries.
    Verticality is strictly weaker than fibre minimality: a vertical symmetry may enlarge the
    fibre without changing the image.
    The replacement of the sufficient condition (O18) by the necessary and sufficient condition
    (O24) therefore strictly extends the scope of the programme: the chain
    $\cchi \to \dpair \to \bstar$ holds not only when fibres are minimal, but whenever
    additional fibre structure acts vertically.

  \subsection{Vertical versus transversal non-injectivity}
    \label{sec:vertrans}

    The distinction between vertical and transversal non-injectivity is the structural principle
    underlying the present paper.
    It can be stated as a single invariance property:

    \begin{quote}
      \textbf{Observable rank rigidity under admissible non-injectivity.}
      \emph{The real rank of $\operatorname{Im}\Pi \cap \Ntrl$ is a protected invariant:
        $\ker\Pi$ may change freely; $\operatorname{Im}\Pi \cap \Ntrl$ is rigid.}
    \end{quote}

    \emph{Vertical non-injectivity} means that multiple substrate configurations project to the
    same observable.
    This increases the microscopic degeneracy --- the number of configurations in each fibre ---
    but leaves the observable sector unchanged.
    Its physical effect is an increase in the amplitude of projection residuals, manifest as
    fluctuations in the effective description.

    \emph{Transversal non-injectivity} would mean that $\Pi$ fails to distinguish configurations
    that differ in the observable sector.
    This would collapse independent observable directions and reduce the rank of
    $\operatorname{Im}\Pi \cap \Ntrl$ below~$3$.
    Lemma~\ref{lem:verticality} shows that this case does not arise for any $g \in \GBI$.

    The programme is therefore stable under arbitrary enlargement of the fibres, provided that
    enlargement is vertical.

  \subsection{Fluctuations as kernel-level residuals}
    \label{sec:fluctuations}

    Section~\ref{sec:residuals} identified projection residuals as the physical consequence of
    vertical non-injectivity.
    A larger fibre produces a larger space of substrate configurations that are invisible to
    admissible observables; their contribution appears as fluctuations in the effective
    description.

    Crucially, these fluctuations inhabit the same effective space as the observables.
    They do not create a new sector; they add noise to the existing one.
    The cascade exponent $\dpair$, the saturation rank $n_3$, and the threshold condition
    $\Sigma_c(n_3) = 3$ are all properties of the observable sector and are unaffected by the
    amplitude of projection noise.

    This is consistent with the interpretation developed in O14~\cite{Beau2026a18} Section~6.4,
    where the residual correction $\epsilon(q)$ is identified as the observable imprint of
    projection residuals, controlled by the phase variance $\mathrm{Var}(\theta)(q)$.
    The present result provides the structural justification for this interpretation: projection
    residuals are precisely the kernel-level degrees of freedom of $\Pi$, and their effect on
    observables is bounded by the rank stability established in
    Theorem~\ref{thm:rankstability}.

  \section{Conclusion}
  \label{sec:conclusion}

  The present paper has established that the transfer chain
  $\cchi \to \dpair \to \bstar \approx 0.126$ holds unconditionally with respect to the fibre
  structure of the non-injective projection $\Pi$.
  The key result is the Verticality Lemma (Lemma~\ref{lem:verticality}): every Born--Infeld-admissible
  symmetry acts vertically with respect to $\Pi$, so that no admissible symmetry can enlarge
  the real rank of the observable sector beyond~$3$.

  The argument is non-classificatory.
  It does not enumerate all symmetries of $\SBI$ or classify the full space
  $\mathcal{C}_{\mathrm{eff}}$.
  It uses a single structural obstruction: the quaternionic maximality established in
  O23~\cite{Beau2026a27}, which ensures that no admissible direction of rank greater than~$3$
  can exist.

  The conceptual reorientation relative to O18 is:
  \begin{quote}
    \emph{The condition of O18 required fibres to be small.
    The present result shows that fibre size is physically irrelevant:
    non-injectivity affects degeneracy, not structure.}
  \end{quote}

  With O22, O23, and the present paper, all structural conditionalities in the O-series chain
  are resolved.
  The programme now reduces to a single remaining task: the extended numerical campaign at
  large primes, which will determine whether the shell-alignment prediction is quantitatively
  confirmed and reduce the residual uncertainty in $\dpair$ and $\bstar$.

  \paragraph{Status update (O25 extension to $q = 601$).}
    That campaign has since been carried out in O25~\cite{Beau2026a29}.
    An extended pair-capacity campaign up to $q = 601$ confirms that the transfer parameter
    inferred from the pair observable remains in the expected $0.11$--$0.13$ range, while the
    underlying \emph{raw} exponent $\dpair(q)$ itself descends into the admissible window
    $[7.4, 10.6]$ as $q$ grows --- reaching $\approx 7.6$ at $q = 601$ --- without requiring the
    finite-size normalization correction used on the earliest (small-$q$) datasets.
    The transfer chain $\cchi \to \dpair \to \bstar$ is thereby confirmed numerically; the exact
    asymptotic value $\delta_\infty$ (and hence the precise value of $\bstar$ within that band)
    remains open, as competing convergence laws are not yet distinguished at $q \le 601$.

  \appendix

  \section{Classification of Symmetry Actions: Vertical and Transversal}
  \label{app:examples}

  This appendix collects the three natural candidate classes of additional symmetries of $\SBI$
  and verifies in each case that the action is vertical, supplementing the case analysis of
  Section~\ref{sec:cases}.

  \paragraph{A.1 Parity $\chi \mapsto -\chi$.}
    The Born--Infeld action is even in $\chi$: $\SBI[-\chi] = \SBI[\chi]$.
    Parity therefore belongs to $\GBI$.
    For any observable $o = \Pi(\chi)$, the definition of the fibre ensures
    $\Pi(-\chi) = \Pi(\chi) = o$ (since $-\chi$ and $\chi$ are identified by the Born--Infeld
    indiscernability established in O18~\cite{Beau2026a22}).
    Parity acts vertically.

  \paragraph{A.2 Phase rotation U(1).}
    The substrate field $\chi\colon \mathrm{Heis}_3(\mathbb{Z}/q\mathbb{Z}) \to \mathbb{R}$ is
    real-valued by construction~\cite{Cosmochrony}.
    The Born--Infeld kinetic term $F^2 = (D\chi)^2$ is manifestly real and does not admit a
    U(1) phase symmetry $\chi \mapsto e^{i\theta}\chi$ for $\theta \notin \pi\mathbb{Z}$.
    This class of symmetries is absent from $\GBI$ and requires no further analysis.

  \paragraph{A.3 Topological winding symmetries.}
    The Topological Invariants paper~\cite{Beau2026k} establishes that admissible configurations
    carry discrete topological invariants: charge as a winding invariant (Section~2 of~\cite{Beau2026k}) and spin as
    a covering invariant (Section~3 of~\cite{Beau2026k}).
    Two configurations with distinct winding numbers are distinguished by $\Pi$: they project to
    distinct observables.
    A symmetry that would identify them --- mapping a configuration of winding number $w$ to one
    of winding number $w' \neq w$ --- would contradict the discrete classification of~\cite{Beau2026k} and would not
    be compatible with Born--Infeld admissibility.
    Such symmetries are absent from $\GBI$.

    In all three cases, no transversal action on the admissible observable sector arises.
    The verticality of $\GBI$ established in Lemma~\ref{lem:verticality} is therefore consistent
    with the full catalogue of natural candidate symmetries.

    \clearpage
    \begin{thebibliography}{99}
      \input{cosmochrony-bibliography}
    \end{thebibliography}

\end{document}
